Treefelling_test_for all trees

### 2021-07-28 R/Treefelling_test_for all trees.Rmd
Corrections (cleaninventory)
Treefelling

# INPUTS
```{r Give values to the arguments to work}
data(Paracou6_2016)
data(DemParacou)

inventory <- addtreedim(cleaninventory(inventorycheckformat(Paracou6_2016)))

@@

```{r}
felling <- function (inventory, SelectedTrees, fuel, directionalfelling, advancedloggingparameters = loggingparameters()) {

@@

  # For a random direction felling
  if(directionalfelling == "0" && (fuel !="1" |fuel !="2")){
    RandomAngle <- sample(c(0:180), size = 1)
    TrunkA <- RotatePolygon(Trunk, angle = RandomAngle, fixed = Foot) # turned trunk
    CrownA <- RotatePolygon(Crown, angle = RandomAngle, fixed = Foot) # turned crown
    TrunkB <- NULL
    CrownB <- NULL
  }

@@

  # To direct to avoid damage to future and reserve trees + track orientation. Winching: Foot before.
  if(directionalfelling == "2"&& (fuel !="1" |fuel !="2")){
    TrunkA <- RotatePolygon(Trunk, angle = 240 + theta, fixed = Foot) # turned trunk
    CrownA <- RotatePolygon(Crown, angle = 240 + theta, fixed = Foot) # turned crown
    TrunkB <- RotatePolygon(Trunk, angle = 120 + theta, fixed = Foot) # turned trunk 
    CrownB <- RotatePolygon(Crown, angle = 120 + theta, fixed = Foot) # turned crown
  }

@@

    if(TrailDist <= advancedloggingparameters$GrappleLength){ # <= 6m (= grapple length) -> winching by grapple
      TrunkA <- RotatePolygon(Trunk, angle = theta + 60 , fixed = Foot) # turned trunk
      CrownA <- RotatePolygon(Crown, angle = theta + 60 , fixed = Foot) # turned crown
      TrunkB <- RotatePolygon(Trunk, angle = 300 + theta, fixed = Foot) # turned trunk
      CrownB <- RotatePolygon(Crown, angle = 300 + theta, fixed = Foot) # turned crown
    } else { # > 6m -> winching by cable
      TrunkA <- RotatePolygon(Trunk, angle = 240 + theta, fixed = Foot) # turned trunk
      CrownA <- RotatePolygon(Crown, angle = 240 + theta, fixed = Foot) # turned crown
      TrunkB <- RotatePolygon(Trunk, angle = 120 + theta, fixed = Foot) # turned trunk 
      CrownB <- RotatePolygon(Crown, angle = 120 + theta, fixed = Foot) # turned crown
    }

@@

  FellingOuputs <- list(a = a,
                        Foot = Foot,
                        ScndTrail = ScndTrail,
                        NearestPoints = NearestPoints,
                        Trail = Trail,
                        TrunkA = TrunkA,
                        CrownA = CrownA,
                        TrunkB = TrunkB,
                        CrownB = CrownB)

@@

```{r}
SelectedTrees <- inventory %>% 
  filter(Selected == "1") %>%
  dplyr::select(idTree,DBH,TrunkHeight,TreeHeight,CrownHeight,CrownDiameter,Selected, Xutm, Yutm)

@@

NearestPoints <-  st_union(st_union(AllTheFellingTrees[[1]]$NearestPoints, AllTheFellingTrees[[2]]$NearestPoints), AllTheFellingTrees[[3]]$NearestPoints)
# Trail <- Trail
TrunkA <- st_union(st_union(AllTheFellingTrees[[1]]$TrunkA, AllTheFellingTrees[[2]]$TrunkA), AllTheFellingTrees[[3]]$TrunkA)

CrownA <- st_union(st_union(AllTheFellingTrees[[1]]$CrownA, AllTheFellingTrees[[2]]$CrownA), AllTheFellingTrees[[3]]$CrownA)

TrunkB <- st_union(st_union(AllTheFellingTrees[[1]]$TrunkB, AllTheFellingTrees[[2]]$TrunkB), AllTheFellingTrees[[3]]$TrunkB)

CrownB <- st_union(st_union(AllTheFellingTrees[[1]]$CrownB, AllTheFellingTrees[[2]]$CrownB), AllTheFellingTrees[[3]]$CrownB)

ggplot() + # plot 2 polygones
  geom_sf(data = a, colour = "red") + # default tree position (polygone)
  geom_sf(data = Foot) + # the foot of the tree (point)
  geom_sf(data = ScndTrail) + # the 2nd trail (polygone)
  geom_sf(data = NearestPoints) + # the shortest way from the foot to the trail
  # geom_sf(data = Trail) + # the point on the ScndTrail closest to the location of the tree (Foot)
  geom_sf(data = TrunkA, colour = "green") + # Foot before
  geom_sf(data = CrownA, colour = "green") +
  geom_sf(data = TrunkB, colour = "green") +
  geom_sf(data = CrownB, colour = "green")

>>>>

# INPUTS
```{r Give values to the arguments to work}

inventory <- addtreedim(inventorycheckformat(Paracou6_2016))

@@

# Succès-échec
```{r}
# Selected <-  Accessible

successfail <- function(
  inventory,
  fuel = "2",
  directionalfelling = "2",
  advancedloggingparameters = loggingparameters()) {

  if (fuel == "0" && directionalfelling != "1"){
    inventory <- inventory %>% 
      mutate(TreeFellingOrientationSuccess = ifelse(Selected == "1", sample(c(1,0), size = 1, replace = F, prob = c(advancedloggingparameters$TreefallSuccessProportion, 1-advancedloggingparameters$TreefallSuccessProportion)), NA)) # Accessible = linked by 2ndtrails

    #Tree coordinates 
    if (any(inventory$TreeFellingOrientationSuccess == "1", na.rm = TRUE)) {

      TreefallSuccessCoord <- inventory %>% 
        filter(TreeFellingOrientationSuccess == "1") %>% 
        select(Xutm, Yutm)

      TreefallSuccess  <- st_multipoint(x = as.matrix(TreefallSuccessCoord))   # Create treefelling success
    }

    if (any(inventory$TreeFellingOrientationSuccess == "0", na.rm = TRUE)) {
      TreefallFailCoord <- inventory %>% 
        filter(TreeFellingOrientationSuccess == "0") %>% 
        select(Xutm, Yutm)

      TreefallFailure  <- st_multipoint(x = as.matrix(TreefallFailCoord))      # Create treefelling fails

  if (fuel =="1") {

    inventory <- inventory %>% 
      mutate(TreeFellingOrientationSuccess = ifelse(Selected == "1", sample(c(1,0), size = 1, replace = F, prob = c(advancedloggingparameters$TreefallSuccessProportion, 1-advancedloggingparameters$TreefallSuccessProportion)), NA)) # Selected = not yet linked by 2ndtrails, because 2ndtrails came after

    #Tree coordinates 
    if (any(inventory$TreeFellingOrientationSuccess == "1", na.rm = TRUE)) {

      TreefallSuccessCoord <- inventory %>% 
        filter(TreeFellingOrientationSuccess == "1") %>% 
        select(Xutm, Yutm)

      TreefallSuccess  <- st_multipoint(x = as.matrix(TreefallSuccessCoord))   # Create treefelling success
    }

    if (any(inventory$TreeFellingOrientationSuccess == "0", na.rm = TRUE)) {
      TreefallFailCoord <- inventory %>% 
        filter(TreeFellingOrientationSuccess == "0") %>% 
        select(Xutm, Yutm)

      TreefallFailure  <- st_multipoint(x = as.matrix(TreefallFailCoord))      # Create treefelling fails

    }
  }

  # Abattre les creux : 
  if (fuel =="2") {

    inventory <- inventory %>% 
      mutate(TreeFellingOrientationSuccess = ifelse(Selected == "1"| ProbedHollow == "1", sample(c(1,0), size = 1, replace = F, prob = c(advancedloggingparameters$TreefallSuccessProportion, 1-advancedloggingparameters$TreefallSuccessProportion)), NA)) # Selected = not yet linked by 2ndtrails, because 2ndtrails came after

    #Tree coordinates 
    if (any(inventory$TreeFellingOrientationSuccess == "1", na.rm = TRUE)) {

      TreefallSuccessCoord <- inventory %>% 
        filter(TreeFellingOrientationSuccess == "1") %>% 
        select(Xutm, Yutm)

      TreefallSuccess  <- st_multipoint(x = as.matrix(TreefallSuccessCoord))   # Create treefelling success
    }

    if (any(inventory$TreeFellingOrientationSuccess == "0", na.rm = TRUE)) {
      TreefallFailCoord <- inventory %>% 
        filter(TreeFellingOrientationSuccess == "0") %>% 
        select(Xutm, Yutm)

      TreefallFailure  <- st_multipoint(x = as.matrix(TreefallFailCoord))      # Create treefelling fails

    }
  }

  treefellingOutputs <- list(inventory = inventory,
                             TreefallSuccess = TreefallSuccess,
                             TreefallFailure = TreefallFailure)

  return(treefellingOutputs)

successfailOutputs <- successfail( #an inventory and 2 multipoints: 1 for success, 1 for fails
  inventory,
  fuel = "2",
  directionalfelling = "2",
  advancedloggingparameters = loggingparameters())

inventory <- successfailOutputs$inventory
```

```{r}
felling <- function (inventory, 
                     SelectedTrees, 
                     fuel, 
                     directionalfelling, 
                     advancedloggingparameters = loggingparameters()
) {

@@

  # For a random direction felling
  if(directionalfelling == "0" && (fuel !="1" |fuel !="2")){
    RandomAngle <- sample(c(0:180), size = 1)
    A <- st_difference(st_union(
      RotatePolygon(Trunk, angle = RandomAngle, fixed = Foot), # turned trunk
      RotatePolygon(Crown, angle = RandomAngle, fixed = Foot) # turned crown
    )) 
    B <- NULL
  }

@@

  # To direct to avoid damage to future and reserve trees + track orientation. Winching: Foot before.
  if(directionalfelling == "2"&& (fuel !="1" |fuel !="2")){
    A <- st_difference(st_union(
      RotatePolygon(Trunk, angle = 240 + theta, fixed = Foot), # turned trunk
      RotatePolygon(Crown, angle = 240 + theta, fixed = Foot) # turned crown
    ))
    B <- st_difference(st_union(
      RotatePolygon(Trunk, angle = 120 + theta, fixed = Foot), # turned trunk 
      RotatePolygon(Crown, angle = 120 + theta, fixed = Foot) # turned crown
    ))
  }

@@

    if(TrailDist <= advancedloggingparameters$GrappleLength){ # <= 6m (= grapple length) -> winching by grapple
      A <- st_difference(st_union(
        RotatePolygon(Trunk, angle = theta + 60 , fixed = Foot), # turned trunk
        RotatePolygon(Crown, angle = theta + 60 , fixed = Foot) # turned crown
      ))
      B <- st_difference(st_union(
        RotatePolygon(Trunk, angle = 300 + theta, fixed = Foot), # turned trunk
        RotatePolygon(Crown, angle = 300 + theta, fixed = Foot) # turned crown
      ))
    } else { # > 6m -> winching by cable
      A <- st_difference(st_union(
        RotatePolygon(Trunk, angle = 240 + theta, fixed = Foot), # turned trunk
        RotatePolygon(Crown, angle = 240 + theta, fixed = Foot) # turned crown
      ))
      B <- st_difference(st_union(
        RotatePolygon(Trunk, angle = 120 + theta, fixed = Foot), # turned trunk 
        RotatePolygon(Crown, angle = 120 + theta, fixed = Foot) # turned crown
      ))
    }

@@

  FellingOuputs <- list(a = a,
                        Foot = Foot,
                        ScndTrail = ScndTrail,
                        NearestPoints = NearestPoints,
                        Trail = Trail,
                        A = A,
                        B = B)

@@

# Application
```{r}
SelectedTrees <- inventory %>% 
  filter(Selected == "1") %>%
  dplyr::select(idTree,DBH,TrunkHeight,TreeHeight,CrownHeight,CrownDiameter,Selected, Xutm, Yutm)

@@

NearestPoints <-  st_union(st_union(AllTheFellingTrees[[1]]$NearestPoints, AllTheFellingTrees[[2]]$NearestPoints), AllTheFellingTrees[[3]]$NearestPoints)
# Trail <- Trail
A <- st_union(st_union(AllTheFellingTrees[[1]]$A, AllTheFellingTrees[[2]]$A), AllTheFellingTrees[[3]]$A)

B <- st_union(st_union(AllTheFellingTrees[[1]]$B, AllTheFellingTrees[[2]]$B), AllTheFellingTrees[[3]]$B)

ggplot() + # plot 2 polygones
  geom_sf(data = a, colour = "red") + # default tree position (polygone)
  geom_sf(data = Foot) + # the foot of the tree (point)
  geom_sf(data = ScndTrail) + # the 2nd trail (polygone)
  geom_sf(data = NearestPoints) + # the shortest way from the foot to the trail
  # geom_sf(data = Trail) + # the point on the ScndTrail closest to the location of the tree (Foot)
  geom_sf(data = A, colour = "green") + # Foot before
  geom_sf(data = B, colour = "green")
